---
title: Skills Transfer
author: Kobus Huisamen
draft: TRUE
date: '2020-06-08'
slug: skills-transfer
categories:
  - skills
  - clusterering
tags:
  - ILS
---

# This is a sample

The current.....

## Problem

How can we know which tasks to transfer (see some lessons in skill transfer from informs conference)

How R helped to solve this problem

Where can we use this 

Sample code and illustration of application of this approach.

## Clustering

We are using clustering k-means --- explain how it works



## Case Study

Link to a shiny app where user can change the number of support levels (cluster)
Generate example data that use skills etc for maintenance tasks


# Create Sample Data

For this we will create a list of tasks and then link all the resources we need for the task.

  * Parts
  * Tools
  * Skills

Depth of maintenance range from A - D
We will pre-assign skills to depth of maintenance, that way we know some skills are normally associated with a specific task complexity.

You cannot give somebody tools and expect them to know what to do with it, but have to teach to transfer skills. Sometimes it takes time to build up the experience.

```{r}
#Generate a task list with random complexity depth
tasks <- 100
task_list <- data.frame(task = paste("Task", seq.int(1,to = tasks,  by = 1)),
                        task_depth = sample(x = c('A','B','C','D'), size = tasks, replace = TRUE))

# Create Resource list
parts <- 50
parts_list <-  paste0("Part-", seq.int(1,to = parts,  by = 1))

tools <- 20
tools_list <-  paste0("Tool-", seq.int(1,to = tools,  by = 1))

skills <- 10
skills_list <-  paste0("Skill-", seq.int(1,to = skills,  by = 1))
skills_level <- sample(x = c('A','B','C','D'), size = skills, replace = TRUE)

#  Link Tasks and Resources


task_resources <- NULL
set.seed(31052020)
for (task in task_list$task) {
  
  #id task complexity
  depth <- task_list[task_list$task==task,'task_depth'] 
  # pick items
  pick_list <- data.frame(task = task, 
                          resource = unique(sample(x = parts_list, size = sample(1:10,1), replace = TRUE)),
                          resource_type = 'part')
  # add pick list to the data
  task_resources <- rbind(task_resources, pick_list)
  
  
  # pick tools
  pick_list <- data.frame(task = task, 
                          resource = unique(sample(x = tools_list, size = sample(1:5,1), replace = TRUE)),
                          resource_type = 'tool')
  # add pick list to the data
  task_resources <- rbind(task_resources, pick_list)
  
  # pick skills
  pick_list <- data.frame(task = task, 
                          resource = unique(sample(x = skills_list[skills_level==depth], size = sample(1:5,3), replace = TRUE)),
                          resource_type = 'skill')
  
  # add pick list to the data
  task_resources <- rbind(task_resources, pick_list)
  
}

#TODO: Show some sample with table
```

So now we have tasks and resources linked

to make heat map make a matrix of tasks vs the resource

```{r}
mm <- model.matrix(task ~., data = task_resources)[,-1]
# heatmap(mm)
library(dplyr)
mm.grp <-  as.data.frame(mm) %>%
  # cbind(meid = df$meid)%>%
  group_by(task_resources$task) %>%
  summarise_all(sum)
#Cluster and dimension reduction
set.seed(1234)
kmeansObj <- kmeans(mm.grp[,-1], 3)
# add cluster
mk <- cbind(mm.grp, cluster = kmeansObj$cluster, depth = task_list$task_depth)
# table(mk$cluster, mk$depth)
heatmap(table(mk$cluster, mk$depth))
# heatmap(as.matrix(mk[,-1]))


```
What we see in heatmap.  Depth A is mainly cluster 1, Depth C has heavy presence in cluster 1 and 2. Depth D is mainly cluster 3. Depth B is almost equally distributed in cluster 2 and 3. 

We can see that there is an opportunity at depth B to transfer skills capability between levels 2 and three. We can identify the tasks for this opportunity. (Skill 3 is common, which mean parts and tools migh be different.)
```{r}
# Task 16
task_resources[task_resources$task %in% c("Task 16", "Task 17"),]
```



Add cluster id to task list

```{r}
task_list$cluster <-  kmeansObj$cluster
```

__Why is that we see some tasks have different complexity but in the same cluster?__
Sample two tasks from same cluster, but different complexity and view difference in resources.

```{r}
# Use kmeansObj$centers to show distance betwwen 
```
